---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## countMissingValues

<!-- badges: start -->
<!-- badges: end -->

The goal of countMissingValues is to count missing values for all columns by group (given a data frame and column name for the group). Below shows some examples of how it can be used. You can also keep the output grouped by the grouping column by using the `.groups` argument. Package dependency involves dplyr.

## Installation

You can install the development version of countMissingValues from [GitHub](https://github.com/) with:
```{r}
#install.packages("devtools")
devtools::install_github("stat545ubc-2023/countMissingValues")
```

## Examples

This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column. 
```{r}
library(countMissingValues)

count_all_missing_by_group(airquality, Month)
```


This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function. 
```{r}
airquality |> count_all_missing_by_group(Month) 
```


The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples. 
```{r}
count_all_missing_by_group(airquality, Month, .groups = "keep")
```

